\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../packages/Comments}
\input{../packages/Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 12\\
Ayman Akhras & 9\\
Nathan Luong & 10\\
Patrick Zhou & 8\\
Kelly Deng & 8\\
Reza Jodeiri & 10\\
\bottomrule
\end{tabular}
\end{table}


The team had a total of 12 meetings over the period of interest. The high number of meetings was due to the need for frequent communication and collaboration to ensure that the project was on track. The team met to discuss the progress of the project, assign tasks, and review the work completed by each team member. The team also met to discuss the VnV plan, VnV report, and other project documents to ensure that they were completed on time and met the requirements of the project.

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 1\\
Ayman Akhras & 1\\
Nathan Luong & 1\\
Patrick Zhou & 1\\
Kelly Deng & 1\\
Reza Jodeiri & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 0\\
Ayman Akhras & 0\\
Nathan Luong & 0\\
Patrick Zhou & 0\\
Kelly Deng & 0\\
Reza Jodeiri & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 9\\
Ayman Akhras & 5\\
Nathan Luong & 0\\
Patrick Zhou & 0\\
Kelly Deng & 0\\
Reza Jodeiri & 4\\
\bottomrule
\end{tabular}
\end{table}

Ayman and Reza lead the communication with the TA, and were responsible for discussing the project with the TA. The other team members were in call and participated in the discussion, but Ayman and Reza were the ones who then asked the other team members questions to the TA.
\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 293 & 100\% \\
Ayman Akhras & 59 & 20\%\\
Kelly Deng & 45 & 15\%\\
Nathan Luong & 59 & 20\%\\
Patrick Zhou & 28 & 10\%\\
Reza Jodeiri & 102 & 35\%\\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ayman Akhras & 1 & 4 \\
Kelly Deng & 0 & 3 \\
Patrick Zhou & 1 & 9 \\
Nathan Luong & 3 & 4 \\
Reza Jodeiri & 30 & 10 \\
\bottomrule
\end{tabular}
\end{table}

The numbers in the "Authored (O+C)" column are low for most team members because the majority of the issues were created and closed by Reza Jodeiri during a team meeting, who took the lead in issue tracking and management. The "Assigned (C only)" column shows a more balanced distribution, indicating that while Reza created most of the issues, the tasks were distributed among the team members for resolution. Some of these Issues were not tracked on the issue tracker, but were discussed and resolved during team meetings.


\end{document}