\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../packages/Comments.tex}
\input{../packages/Common.tex}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

The POC demo will showcase the end-to-end functionality of our Chest X-Ray analysis app, including Docker containerization, model-based disease prediction, and CI/CD automation. We’ll start with the front-end where users upload X-ray images, then move to the backend where images are normalized, processed through a pre-trained TorchXRayVision model, and a disease label is returned. The key features are:
\begin{itemize}
    \item[-] Docker containerization: Docker: Consistent environments for front-end, backend, and model and use of docker compose to orchestrate the services.
    \item[-] Model-based disease prediction: Model Prediction: pretrained model for X-ray disease detection.
    \item[-] UI : User-friendly interface for uploading X-ray images.
    \item[-] Modular backend: a modular backend that can be easily extended to support additional models for disease prediction.
    \item[-] CI/CD Pipeline: Automated testing and deployment with GitHub Actions.
\end{itemize}

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 9\\
Ayman Akhras & 7\\
Kelly Deng & 9\\
Patrick Zhou  & 8\\
Nathan Luong & 9\\
Reza Jodeiri& 9\\
\bottomrule
\end{tabular}
\end{table}

\begin{itemize}
    \item[-] As we divided the team into subteams for developing the different components of the project; therefore, some members were not required to attend all meetings.
\end{itemize}

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Ayman Akhras & 1\\
Kelly Deng & 2\\
Patrick Zhou  & 2\\
Nathan Luong & 2\\
Reza Jodeiri& 2\\
\bottomrule
\end{tabular}
\end{table}

\begin{itemize}
    \item[-] Ayman missed one of the meetings due to sickness.
    \item[-] We are currently following a montly meeting schedule with our supervisor, Dr.Moradi.
\end{itemize}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 11\\
Ayman Akhras & 7\\
Kelly Deng & 8\\
Patrick Zhou  & 8\\
Nathan Luong & 9\\
Reza Jodeiri& 5\\
\bottomrule
\end{tabular}
\end{table}

\begin{itemize}
    \item[-] Most team members were not able to attend the lecture on VNV-Plan as there was a SFWRENG 4X03 midterm scheduled right after lecture.
    \item[-] Reza is on a co-op term and was not able to attend all lectures as the lectures were scheduled during his work hours.
    \item[-] Ayman missed a few lectures due to illness.
\end{itemize}

\section{TA Document Discussion Attendance}

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    Total & 3\\
    Ayman Akhras & 3\\
    Kelly Deng & 3\\
    Patrick Zhou  & 3\\
    Nathan Luong & 3\\
    Reza Jodeiri& 3\\
    \bottomrule
    \end{tabular}
    \end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 131 & 100\% \\
Ayman Akhras & 15 & 11\% \\
Kelly Deng & 20 & 15\% \\
Patrick Zhou & 20 & 15\% \\
Nathan Luong & 24 & 18\% \\
Reza Jodeiri & 52 & 41\% \\
\bottomrule
\end{tabular}
\end{table}

\noindent These are approximate values as there are unmerged branches that have not been accounted for.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ayman Akhras & 0 & 19 \\
Kelly Deng & 0 & 19\\
Patrick Zhou & 1 & 19 \\
Nathan Luong & 2 & 22 \\
Reza Jodeiri & 23 & 26 \\
\bottomrule
\end{tabular}
\end{table}


\section{CICD}

Our project uses GitHub Actions for continuous integration and deployment and the pipeline is triggered on every push to the repository. The pipeline runs the tests and deploys the application.Here is  what the pipeline does:
\begin{itemize}
    \item[-] Builds the Docker image: Creates a Docker image for the application using the latest code and configuration, ensuring a consistent runtime environment for testing and deployment..
    \item[-] Runs unit tests: Executes all unit tests to validate individual components of the application, ensuring that new changes don’t break existing functionality.
    \item[-] Applies code quality checks using linters and static analysis tools such as Pylint to enforce coding standards and detect potential issues, which helps maintain readability and consistency across the codebase.
    \item[-] Deploys the Docker image to our registery, allowing developers to access latest stable version of the application after all tests pass successfully.
\end{itemize}

\end{document}